\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{geometry, changepage}
\usepackage{amsmath, amssymb, amsthm, bm}
\usepackage{physics}
\usepackage{hyperref}

\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=cyan}
\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{claim}{Claim}
\newtheorem*{theorem*}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem*{claim*}{Claim}

\title{MATH-UA 140: Assignment 0}
\author{James Pagan, September 2023}
\date{Professor Raquépas}

% --------------------------------------------- %

\begin{document}

\maketitle

% --------------------------------------------- %

\textbf{Write a brief note to the instructional team in the space below listing anything about you as a student that you would like us to know.}

\begin{itemize}
	\item I am a freshman familiar with olympiad math and (the first course content of) modern algebra and real analysis, fluent in proofwriting. I will also submit assignments on \LaTeX --- if the instructional team permits as such. 
\end{itemize}

\textbf{What are the two known exam dates so far?}

\begin{itemize}
	\item The two exam dates are October 19 and November 16; the date of final is yet to be announced.
\end{itemize}

\textbf{What recitation section are you enrolled in, and who is your TA?}

\begin{itemize}
	\item I am enrolled in Section 026, taught by Santi Aranguri Diaz.
\end{itemize}

\textbf{Will curves be applied to the grades of individual assignments or exams?}

\begin{itemize}
	\item No; curves will be applied to final letter grades, but not to individual assignnments or exams.
\end{itemize}

\end{document}
